The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-20 src/ms.tex
Put performance last also in intro.

Within \astropypkg, development may be roughly split into a few categories:
new features added, performance enhancements, intra and inter-package
interoperability, and improvements to precision, accuracy, and
reproducibility. We discuss these in turn.

>>>>

Within \astropypkg, development may be roughly split into a few
categories: new features added, intra and inter-package
interoperability, improvements to precision, accuracy, and
reproducibility, and performance enhancements. We discuss these in turn.
